Constraints on Assembly Bias from Galaxy Clustering.

### 2016-06-07 ms.tex
and yet more
this time describing observational evidence for assembly bias

The ultimate goal of halo occupation modeling is to characterize the
galaxy-dark matter connection by constraining the probability
distribution $P(X_{\rm g}|Y_{\rm h})$. Here $X_{\rm g} = {x_1, x_2,
  ...x_n}$ is a set of $n$ galaxy properties, and $Y_{\rm h} = {y_1,
  y_2,...,y_m}$ a set of $m$ halo properties. Accurate knowledge of
this probability distribution yields invaluable insight to the
processes of galaxy formation, and allows one to make accurate
predictions for the clustering of galaxies as function of any property
$x_i$. Most halo occupation studies to date have restricted themselves
to only one halo property, namely halo mass.  This includes all Halo
Occupation Distribution (HOD) models, which aim to constrain
$P(N|\mvir)$, the probability that a halo of mass $M$ contains $N$
galaxies of some specified properties
\citep[e.g.,][]{kauffmann_etal97,jing98,benson01,berlind02}, and all
Conditional Luminosity Function (CLF) models, which aim to constrain
$\Phi(L|M)$, the luminosity (or stellar mass) function of galaxies in
haloes of mass $M$ \citep[e.g.,][]{yang03,vdBosch03a,cooray06}. The
HOD and CLF models are mainly used in combination with the halo model,
which describes the non-linear matter field in terms of halo building
blocks \citep[e.g.,][]{seljak00,cooray02}, to predict the clustering
of galaxies as function of luminosity or stellar mass.  Although
entirely analytical, and therefore fast, the downside of this method
is that it is extremely challenging to construct a model that is
accurate at the few percent level. The main issues are halo exclusion
\citep[see][]{smith_etal07,vdBosch13}, scale dependence of the
halo bias \citep[see][]{tinker05}, and the halo assembly bias mentioned
above.

@@

>>>>

The ultimate goal of halo occupation modeling is to characterize the
galaxy-dark matter connection by constraining the probability
distribution $P(X_{\rm g}|Y_{\rm h})$. Here $X_{\rm g} = {x_1, x_2,
  ...x_n}$ is a set of $n$ galaxy properties, and $Y_{\rm h} = {y_1,
  y_2,...,y_m}$ a set of $m$ halo properties. Accurate knowledge of
this probability distribution yields invaluable insight regarding the
processes of galaxy formation, and allows one to make accurate
predictions for the clustering of galaxies as function of any property
$x_i$. Most halo occupation studies to date have restricted themselves
to only one halo property, namely halo mass.  This includes Halo
Occupation Distribution (HOD) models, which aim to constrain
$P(N|\mvir)$, the probability that a halo of mass $M$ contains $N$
galaxies of some specified properties
\citep[e.g.,][]{kauffmann_etal97,jing98,benson01,berlind02}, and
Conditional Luminosity Function (CLF) models, which aim to constrain
$\Phi(L|M)$, the luminosity (or stellar mass) function of galaxies in
haloes of mass $M$ \citep[e.g.,][]{yang03,vdBosch03a,cooray06}. The
HOD and CLF models are mainly used in combination with the halo model,
which describes the non-linear matter field in terms of halo building
blocks \citep[e.g.,][]{seljak00,cooray02}, to predict the clustering
of galaxies as function of luminosity or stellar mass.  Although
entirely analytical, and therefore fast, the downside of this method
is that it is extremely challenging to construct a model that is
accurate at the few percent level. The main issues are halo exclusion
\citep[see][]{smith_etal07,vdBosch13}, scale dependence of the halo
bias \citep[see][]{tinker05}, and the halo assembly bias mentioned
above.

@@

Additional support for the presence of assembly bias has come from a
variety of studies that have shown, or suggested, that the large-scale
environment (i.e., clustering strength) of dark matter haloes {\it of
  fixed mass} is correlated with the star formation rate of their
central
galaxies\citep[][]{yang_etal06a,blanton_berlind07,wang_etal08,tinker_etal12,wang_etal13,HW13a,hearin_etal13b,hearin_etal14,watson_etal14}.
However, a recent study by \citet{lin_mandelbaum_etal15} argues that
most of the these differences in clustering strength can be explained
as due to differences in halo mass or contamination by satellite
galaxies. \citet{lin_mandelbaum_etal15} therefore argue that there is
no significant evidence for assembly bias in galaxy-scale halos
\citep[see also][]{paranjape15}.

\citet{yang_etal06a}, who showed that the clustering strength of
galaxy groups (i.e., dark matter haloes) of fixed mass is correlated
with the star formation rate of their central galaxy. Similar
conclusions have been reached by a number of independent
studies\citep[][]{blanton_berlind07,wang_etal08,tinker_etal12,wang_etal13,hearin_etal14}. However,
\citet{lin_mandelbaum_etal15} have argued that these differences in
clustering strength can all be explained as due to differences in halo
mass or contamination by satellite galaxies and concluded that there
is no significant evidence for assembly bias in galaxy-scale halos
\citep[see also][]{paranjape15}.

In addition, Hearin etal have argued that the large-scale conformity
in galaxy star formation rates observed by Kauffmann etal is another
`smoking-gun' signature of assembly bias (but see Parajape etal 2015).

halos with quenched centrals are
more strongly clustered than halos of the same mass that host star
forming centrals \citep[see
  also][]{blanton_berlind07,wang_etal08,wang_etal13}

Using galaxy-group cross correlations, Ref. [61] has shown that halos
with quenched centrals are more strongly clustered than halos of the
same mass that host star forming centrals. This first observational
evidence for galaxy assembly bias has been confirmed using larger data
sets [62, 63]. F

Further evidence for assembly bias from group catalogs
has come from Ref. [64], who found that the color/SFR of satellite
galaxies depend on the color/SFR of the group’s central galaxy, again
at fixed halo mass, a phenomenon dubbed galactic conformity.  More
recently, Ref. [65] demonstrated that correlations between the SFRs of
central galaxies and their neighboring galaxies persist out to many
Mpc, far beyond the virial radii of their host halos.  Quenched
central galaxies preferentially reside in large-scale environments
replete with quenched galaxies. Both these conformity signals indicate
manifest violations of the Mass-Only ansatz [66].  A different
approach was taken by Ref. [67], who shuffled the colors and
luminosities of galaxies in groups of similar mass, preserving for
each galaxy its group-centric distance. This procedure preserves the
halo occupation N|Mh, but erases the relationship between the
galaxies and the larger-scale environments of the groups in which they
reside. The Mass-Only ansatz predicts that the real and shuffled group
catalogs should reveal identical clustering. Contrarily, the
clustering in the two catalogs differ at the ∼ 5% (∼ 10%) level on
scales larger
                                     % (smaller) than ∼ 1 h
